The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-14 paper.tex
more revisions

 As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically. Surprisingly, an entanglement between a large number of spatial modes is possible with single photons in a passive linear optical device. This so-called number-path entanglement can be harnessed for quantum metrology without the use of entangled states like the NOON state \cite{bib:Motes15}. Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig. \ref{fig:MORDOR}). By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve 
\begin{align}
\Delta \varphi=\mathcal{O}\left(\frac{1}{N^{3/2}}\right) \ ,	
\end{align}
with just a string of $N$ single photons, one photon per mode, for up to at least $N=25$ modes.

>>>>

 As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically. Surprisingly, an entanglement between a large number of spatial modes is possible with single photons in a passive linear optical device. This so-called number-path entanglement can be harnessed for quantum metrology without the use of entangled states like the NOON state \cite{bib:Motes15}. Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig. \ref{fig:MORDOR}). By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ with just a string of $N$ single photons, one photon per mode, for up to at least $N=25$ modes.
